Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-30 paper/paper.tex
revise a bit on section 6.1

Readers familiar with functional programming may think of @fold@ at this point; indeed,
it is a variant implementation of @fold@ in continuation-passing style. But here we have two
continuations, one for the next element in the collection, and one for the eventual result.
This is sometimes referred to as an extended continuation-passing style (ECPS)
that function @k@ is a continuation and @m@ is a meta-continuation 
\cite{Danvy:1990:AC:91556.91622}. \\

>>>>

Readers familiar with functional programming may think of @fold@ at this point; indeed,
it is a variant implementation of @fold@ in continuation-passing style. But as we mentioned 
in Section \ref{linear}, here we have two continuations, one continuation @k@ for the next 
element in the collection, and one meta-continuation @m@ for the eventual accumulator.
This is sometimes referred to as an extended continuation-passing style (ECPS) \cite{Danvy:1990:AC:91556.91622}. \\
